\chapter{Arrays and Strings}

\begin{description}
\item[1.1] Implement an algorithm to determine if a string has all unique characters. What if you can not use additional data structures?
\lstinputlisting[language=C++]{ch1one.cpp}
\lstinputlisting[language=python]{ch1one.py}

\item[1.2] Write code to reverse a C-Style String. (C-String means that “abcd” is represented as five characters, including the null character.)
\lstinputlisting[language=C++]{ch1two.cpp}

\newpage
\item[1.3] Design an algorithm and write code to remove the duplicate characters in a string without using any additional buffer. NOTE: One or two additional variables are fine. An extra copy of the array is not. FOLLOW UP Write the test cases for this method.
\lstinputlisting[language=C++, firstline=1, lastline=101]{ch1thr.cpp}

\newpage
\item[1.4] Write a method to decide if two strings are anagrams or not.
\lstinputlisting[language=C++]{ch1for.cpp}

\newpage
\item[1.5] Write a method to replace all spaces in a string with ‘\%20’.
\lstinputlisting[language=C++]{ch1fiv.cpp}

\item[1.6] Given an image represented by an NxN matrix, where each pixel in the image is 4 bytes, write a method to rotate the image by 90 degrees. Can you do this in place?
\lstinputlisting[language=C++]{ch1six.cpp}

\item[1.7] Write an algorithm such that if an element in an MxN matrix is 0, its entire row and column is set to 0.
\lstinputlisting[language=C++]{ch1sev.cpp}

\item[1.8] Assume you have a method isSubstring which checks if one word is a substring of another. Given two strings, s1 and s2, write code to check if s2 is a rotation of s1 using only one call to isSubstring (i.e., “waterbottle” is a rotation of “erbottlewat”).
\lstinputlisting[language=C++]{ch1eit.cpp}

\end{description}
